```{r setup, include=FALSE}
setwd( "/Users/hun/Library/CloudStorage/OneDrive-SNU/1. University/UChicago/2022 4Q Winter/TimeSeries_Ruey/ts_ruey_R/final")
require(MTS)
require(urca)
require(fUnitRoots)
require(tsDyn)
library(doMC)
registerDoMC(5)

data = read.csv("sp500_etf.csv")
vecm_res = read.csv("result/vecm_res.csv")
date = data[,1]
prices = data[,2:ncol(data)]
```

```{r}
get_vecm_data = function(pair_name, y){
    pair_name1 = paste("('", pair_name[1], "', '", pair_name[2], "')", sep = "")
    pair_name2 = paste("('", pair_name[2], "', '", pair_name[1], "')", sep = "")
    sub_res = vecm_res[which(vecm_res['year']== y),]
    sub_res = sub_res[which((sub_res['pair'] == pair_name1) | (sub_res['pair'] == pair_name2)),]
    return (sub_res)
}

get_sample = function(y) {
    start = as.character(strtoi(y) - 2)
    start_end = as.character(strtoi(y) - 1)
    df_in = prices[which((yy == start) | (yy == start_end)),]
    df_out = prices[which(yy == y),]
    return(list(df_in, df_out))
}

yy = c(rep(0, length(date)))
j=1
for (i in date) {
    yy[j] = substr(i, 1, 4)
    j = j + 1
}
years = unique(yy)

check_vecm = function(df1, df2) {
    res = ca.jo(cbind(df1, df2), type = "trace", ecdet = "none", K = ord, spec = "transitory")
    rt = res@teststat
    cval = res@cval
    if ((rt[1] < cval[1,1]) & (rt[2] > cval[2,3])) {
        return(0.01)
    } else {
        return(1)
    }
}

pair_vecm = function(df_in, y) {
    n = ncol(df_in)
    result = matrix(NaN, nrow = n, ncol = n)
    combs = combn(1:n, 2)
    for (i in 1:ncol(combs)) {
        j = combs[,i]
        r = check_vecm(df_in[j[1]], df_in[j[2]])
        result[j[1], j[2]] = r
    }
    colnames(result) = colnames(df_in)
    rownames(result) = colnames(df_in)
    return(result)
}

check_tvecm = function(df, ord) {
    res = TVECM.HStest(df, lag = ord, intercept = F, ngridTh = 50, hpc ='foreach')
    return(res$PvalBoot)
}

pair_tvecm = function(df_in, y) {
    n = ncol(df_in)
    result = matrix(NaN, nrow = n*(n-1)/2, ncol = 4)
    combs = combn(1:n, 2)
    for (i in 1:ncol(combs)) {
        j = combs[,i]
        sub_df = df_in[j]
        ns = colnames(sub_df)
        ord = max(get_vecm_data(ns, y)[1, 'order'], 1)
        r = check_tvecm(sub_df, ord)
        tvecm_res = TVECM(sub_df, include = "none", lag = ord, trace = FALSE)
        beta = tvecm_res$model.specific$beta
        result[i,] = c(paste(ns, collapse = "."), y, r, beta)
    }
    colnames(result) = c("pair", "year", "pval", "beta")
    return(result)
}

```

```{r}
res = matrix(NaN, nrow = 0, ncol = 4)
colnames(res) = c("pair", "year", "pval", "beta")
write.table(res,file='result/tvecm_res.csv',sep=',', row.names = FALSE, append=FALSE)

for (y in years[4:length(years)-1]) {
    df_in = get_sample(y)[[1]]
    temp = pair_tvecm(df_in, y)
    write.table(temp, file='result/tvecm_res.csv', sep=',', 
    row.names = FALSE, col.names = FALSE, append=TRUE)
}
```

```

```{r}
check_seo = function(df) {
    start_time <- Sys.time()
    ord = max(get_vecm_data(ns, y)[1, 'order'], 1)
    temp = TVECM(df, include = "none", lag = ord, ngridTh = 50)
    end_time <- Sys.time()
    print(end_time - start_time)
    res = TVECM.SeoTest(df, lag = ord, beta = temp$model.specific$beta, nboot = 100, check = FALSE, hpc ='foreach')
    end_time <- Sys.time()
    print(end_time - start_time)
    return (res)
}
```

```{r}
pairs = as.matrix(read.csv("./candid2015.csv", row.names = 1))
pair = pairs[1,]

```

```{r}
temp = get_sample("2019")
df_in = temp[[1]]
# df_out = temp[[2]]

# pair = c("VV", "SPY")
# pair = c("IWV", "SCHB")
pair = c("IVV", "ITOT")
y = 2015
df_pair = get_sample(y)[[1]][,pair]
# df_pair = df_out[,pair]
```
```{r}
start_time <- Sys.time()
res = TVECM.HStest(df_pair, lag = 4, intercept = F, ngridTh = 50, hpc ='foreach')
end_time <- Sys.time()
print(end_time - start_time)
```

```{r}
seo_res = check_seo(df_pair)
```

```{r}
x = 1:10
x = cbind(x, 2*x+10)
p = 3
# embed(x,p+1)
```

```{r}
temp = function (x, dimension = 1) 
{
    if (is.matrix(x)) {
        n <- nrow(x)
        m <- ncol(x)
        if ((dimension < 1) || (dimension > n)) 
            stop("wrong embedding dimension")
        y <- matrix(0, n - dimension + 1L, dimension * m)
        for (i in seq_len(m)) {
            y[, seq.int(i, by = m, length.out = dimension)] <- Recall(as.vector(x[, 
            i]), dimension)
        }
        return(y)
    }
    else if (is.vector(x) || is.ts(x)) {
        n <- length(x)
        if ((dimension < 1) || (dimension > n)) 
            stop("wrong embedding dimension")
        m <- n - dimension + 1L
        data <- x[1L:m + rep.int(dimension:1L, rep.int(m, dimension)) - 1L]
        print(data)
        dim(data) <- c(m, dimension)
        print(data)
        return(data)
    }
    else stop("'x' is not a vector or matrix")
}

temp(x, 3)
```
```{r}
y = as.matrix(df_pair)
p = 3
T<-nrow(y)
k<-ncol(y)
Y = t(diff(y))[,(p+1):(T-1)]
DeltaX<-rbind(1,t(embed(diff(y),p+1)[,-(1:k)]))	#trend and lags matrixs DeltaX(t-1,..) of dim: pk x t
ECTfull = y %*% c(1, -0.5)
ECT<-ECTfull[-c(1:p,T)]				#ECT

ECTminus <-ifelse(ECT<155,1,0)*ECT			
ECTplus <-ifelse(ECT>160, 1,0)*ECT
ThreshECT<-cbind(ECTplus, ECTminus)
Zsig<-rbind(ECTminus,ECTplus,DeltaX)
Bsig<-tcrossprod(Y,Zsig)%*%chol2inv(chol(tcrossprod(Zsig)))
resSig<-t(Y-Bsig%*%Zsig)
resb<-rbind(matrix(0,nrow=p, ncol=k),apply(resSig,2,sample, replace=TRUE))
```